---
title: "Programming Background"
author: "Jenna Wilkie"
date: "9/14/2021"

---
```{r}
#code chunk to change image output destination
knitr::opts_chunk$set(fig.path = "../images/")
```

## Prompt:
**Everyone in this course had some programming experience coming in (due to the prerequisites).  What are your thoughts on R vs whatever other software you've used?  What functionality do you like about R?  What parts do you miss about your other language?  Do you consider R a difficult language to learn? (If you knew R prior to the course, describe your experience when first learning it.)**

The first programming language I learned was Python.  When I first started learning R, I thought it was much more difficult than Python.  The syntax used in Python felt much more straightforward.  I also felt the same way about SAS language vs. R.  There are also not as many functions in Python that do the same thing (at least that I know of), so that made it an easier language to pick up in the beginning.  Now that I've had a little more time to get used to R, I like that it has many functions built in for statistical analysis.  I think, of the programming languages I've learned, R was the most difficult.  In terms of statistical analysis, I usually prefer SAS, but R does have some perks.  I really like how easy it is to use the R markdown tool to make reports that include code.   Once I had more time to practice in R, it was not nearly as daunting as when I was first learning it.  

## Example R Markdown Output
```{r plot}
library(Lahman)
plot(Pitching$ER)
```

